Schema Evolution in Interactive Programming Systems

### 2024-08-28 paper.tex
hedge claim about being inspiring

\paragraph{Challenge Problems.}
These dimensions, layers, and variants generate a wide range of configurations for challenge problems, but
our aim is not to cover all of them. Instead we use this perspective to recast a number of
existing challenges in real-world programming systems as instances of the same problem of
schema evolution. The case studies show how well-known solutions or problems in one domain
map to another domain and they also provide and inspiration and a benchmark for
developers of future programming systems.

>>>>

\paragraph{Challenge Problems.}
These dimensions, layers, and variants generate a wide range of configurations for challenge problems, but
our aim is not to cover all of them. Instead we use this perspective to recast a number of
existing challenges in real-world programming systems as instances of the same problem of
schema evolution. The case studies show how well-known solutions or problems in one domain
map to another domain, and we hope they provide an inspiration and a benchmark for
developers of future programming systems.
